---
title: "Serco Maintenance Event Modelling - Clean"
output: html_notebook
---

Summary
-------
This uses the full dataset of fault reports and property information.

We're doing regression because we want to predict a number.  Ideally we want to predict the number of maintenance events a property will experience in a month (or year).

Column Summary for 'Available Bedrooms and Bedspaces' 
-----------------------------------------------------
This a summary of faults at property per month.  There is one row per property (Unclear if there is a row for every property or only rows for properties with faults).

*Property Category* - All accommodation is categorised by its use.  When principals arrive they are placed in 'Initial Accommodation' (IA).  After a defined period of time they are moved into 'Distributed Accommodation' (DA).  There is an additional category of accommodation 'TDA'.
*ASYS* - Unique identifier for the property.
*Address* - The address of the property.
*Town* - Postal town of the property.
*Postcode* - Postcode associated with the property.
*Ward* - The electoral ward that the property is in.  This has political implications as there are limits placed on Serco in certain wards as to how many properties they can operate(?)
*Property Type* - Categorisation of the type of property. (Block, Bungalow, Detached, Flats-Apartments, G4S, Maisonette, Semi-Detached, Terraced).
*HMO* - Not sure  (Family, HMO, HMO Restrictions)
*Fire Alarm Type* - The type of fire alarm installed in the property. (Battery, Grade A LD2, LD2, LD3)
*Occupancy Type* - The type of occupancy that the property currently has (?).  (Couples, Family, Mum and Baby, Mum and Child <10, Singles Female, Singles Male)
*Housing Officer* - The name of the housing officer responsible for the property. (Well coded - no data entry errors).
*HO Phone Number* - Phone number of the housing office responsible for the property.  (Well coded).
*Property Status* - The status of the property in the Serco system (Active, Awaiting Withdrawal, Coming on line)
*Bed rooms* - The number of bedrooms in the property.  Numeric. Well coded.
*Bedspaces* - number of beds in the property.  Numeric. Well coded.
*Frozen* - number of bedspaces in the property that are frozen in the property.  (frozen means cannot be used).
*Reason for frozen* - The reason that bedspaces in the property are frozen.  Well coded.
*Active Service Users* - The number of service users that are resident in the property.  Numeric.
*Active Service Users Plus* - ?  Numeric.
*Available Bedrooms* - The number of unoccupied bedrooms in the property?  (Lots of negative values.  Why?)
*Available Bedspaces* - The number of unoccupied bed spaces in the property?  (Lots of negative values.  Why?)
*Occupancy* - The number of service users in the property.  (does .5 value mean a child?)
*Landlord Company Name* - The name of the landlord.  Well coded.
*Landlord Name* - The name of the landlord.  Reasonably well coded.  Likely to exclude.
*Landlord Telephone Number* - The telephone number of the landlord.  Likely to exclude.
*Landlord Email address* - The email address of the landlord.  Likely to exclude.
*Rent* - The amount charged monthly for the property.  (May be worth excluding or 'binning').
*Lease Type* - The type of lease applied to the property.  Some blank.  Possibly worth including.
*HMO Potential* - Number of service users that could be added to the property.  Poorly coded.  Exclude.
*No Area Bedrooms* - ??
*No Area Kitchens* - The number of kitchens in the property?
*No Area Kitchen Diners* - The number of kitchen diners in the property?
*No Area Utilities* - The number utility rooms in the property?
*No Area WC s* - The number of toilets in the property?
*No Area Bathrooms* - The number of bathrooms in the property?
*No Area Ensuites* - The number of ensuites in the property?
*No Floors* - The number of floors in the property.
*Floor Plan Available* - Whether a floor plan of the property is available.  Probably exclude.
*Last Departure Date of SU* - Last departure date of service user?
*Days since last departure date* - ??
*Last Booking Date* - ??
*Expected Date of Arrival Relating to Last Booking* - ??
*Last Inspection Date* - The date the property was last inspected.
*Days since last inspection* - Days since the property was last inspected. Generated when the data is exported so needs to be recalcuated when analysis is run from the last inspection date.
*Last Inspection Type* - The type of inspection that was performed when the property was last inspected.  (24hr check, Discontinuation, Dispersal/Relocation, First Housing Officer, Monthly, Onboarding, Quality Audit, Withdrawal)
*Number of Active Faults* - The number of active faults at the property in the reporting period.  These may be historical faults reported in earlier periods that have not been fixed yet.  (Number of historic faults may have an influence on the number of fault reported in the reporting period - broken windows effect).
*Inspection Status* - ?
*Penultimate Inspection Date* - The date of when the property was last inspected.
*Penultimate Inspection Type* - The type of inspection that was performed last time the property was inspected.
*Number of Active faults at Penultimate Inspection Date* - The number of active faults at the property last time it was inspected.

Suspect we want to calculate the number of active faults (or ideally, the number of faults that will be raised this month) - potentially take out the number of active fault last visit.

Column Summary for 'Fault Fix Costings' 
---------------------------------------
This dataset contains a row per fault.  There can be multiple faults per property.

*Fault Reference* - Unique identifier for the fault.  Used by contractor for billing.
*Property Status* - Identifier for if the property is active. (Active, Archived, Awaiting Withdrawal, Coming on line).
*ASYS* - Unique identifier for the property that the fault was reported at.
*Address* - The address of the property where the fault was reported.
*No of Occupants* - The number of occupants at the property where the fault was reported.
*Fault Identified By* - The name of the person who identified the fault.
*Identified Date* - The date and time that the fault was identified.
*Registered Date* - The date and time that the fault was registered on the system.
*Registered By* - The name of the user that registred the fault with the system.
*Date last ammended* - The date and time that the record was last ammended.
*Amended By* - The name of the user that made the last ammendment to the record.
*Housing Officer* - The housing officer responsible for the property.
*Classification* - The classification of the severity of the fault.  Drives how soon the fault should be fixed. (Emergency, Immediate, Monitor, Routine, Urgent).
*Type* - ?? (never completed)
*Other Details* - ?? (never completed)
*Location* - The location that the fault affects.
*Item Category* - The type of item affected by the fault.
*Room Number* - The number of the room in the building that the fault affects. (For multi-room properties).
*Item* - The item affected by the fault.
*Defect* - What is the problem. (Blocked, additional batteries required) slightly random but well coded.
*Issue* - The condition of the defect (Can still be used, cannot be used, etc)  slightly random but well coded.
*Fault Information* - additional fault information.  Looks like free text entry.
*Assigned To* - Who is designated to repair (named individuals as well as generic terms).
*Contractor* - is the work is assigned to a contractor, which contractor (slightly random)
*Maintenance Supervisor* - Who is assigned to supervise the work (7 choices)
*Maintenance Officer* - ?? (38 choices)
*Fault End Date* - ??
*Contract End Date* - The date the fault had to be fixed by???
*Date Fault Fixed* - The date the fault was fixed.
*Fixed By* - The name of the person who fixed the fault.
*Date Service Recovered* - ??
*Date SU Relocated* - The date the service user was relocated (if the fault could not be fixed and required the SU to be moved)?
*Mitigated* - ??
*str CompanyName* - ??
*Service Order Number* - Identifier for the property that the fault affects.  Provides link to landlord data.
*Fault Fix Comments* - Free text
*Inspected By* - Name of person that inspected the fault fix work.
*Inspected Date* - The date and time the fix was inspected.
*Accommodation Type* - The type of the accomodation (Family, HMO, HMO Restrictions)
*Cost* - The cost of the fix.
*Subcontractor* - The name of the subcontractor used for the fix.
*Date Fixed Refined* - Month and year that the fix was done.

*Import Libraries*
```{r}
library("tidyverse")
library("dplyr")
library("plyr")
library(lubridate)
library(stringr)
library(caret)
library(hydroGOF)
library(gbm)
library(xgboost)
library(glmnet)
library("FactoMineR")
library("factoextra")
library(corrplot)

library(caret)
library(corrplot)
library(xgboost)
library(stats)
library(knitr)
library(ggplot2)
library(Matrix)
library(plotly)
library(htmlwidgets)
library(readr)
library(randomForest)
library(data.table)
library(h2o)
library(dplyr)
library(tidyr)
```

Load maintenance events which includes data on the nature of the fault, the fix information and the costs.
```{r}
#maintenanceEvents <- read.csv("csv/Fault Fixed - Costings.csv")

#load the fault fix data
rawMaintenanceEvents <- read.csv("csv/Fault Fixed - Costings - Modified.csv", skip=0, stringsAsFactors = FALSE)
nrow(rawMaintenanceEvents)

#rename 'Address', 'Accommodation.Type' and 'Housing.Officer' fields because they are common to both datasets we will join
names(rawMaintenanceEvents)[names(rawMaintenanceEvents)=="Address"] <- "Event.Address"
names(rawMaintenanceEvents)[names(rawMaintenanceEvents)=="Accommodation.Type"] <- "Event.Accommodation.Type"
names(rawMaintenanceEvents)[names(rawMaintenanceEvents)=="Housing.Officer"] <- "Event.Housing.Officer"


#convert 'Identified.date' date strings to actual dates - We use the lubridate package to parse the datetimes and we use the very useful parse_date_time method because it allow us to specify different format patterns.  This is needed because some of the values in the 'identified date' column have seconds and some dont.  The first format is used for the parsing and if that fails, the second format is used.  Beware that if we just used the second format on a datetime with no seconds it wouldn't error but it would produce the wrong result (the year would be 2020.. which is totally wrong).
#See (https://skgrange.github.io/date_handling.html) for more information.
rawMaintenanceEvents <- mutate(rawMaintenanceEvents, Identified.date= parse_date_time(Identified.date, orders = c("dmy_HM", "dmy_HMS"), tz = "UTC"))
nrow(rawMaintenanceEvents)

#filter to only keep events identified in 2017
#we exclude 2422 rows that have a blank Identified Date or an Identified date that is in 2016
filteredMaintenanceEvents <- filter(rawMaintenanceEvents, Identified.date >= dmy_hms("01-01-2017 00:00:00"))
nrow(filteredMaintenanceEvents)
```

```{r}
#127 rows have invalid ASYS value,including blanks -29 without blanks with values of (DON'T USE, DUPLICATE, DUPLICATE ARCHIVED, TBC)
invalidAsysRows <- subset(filteredMaintenanceEvents, is.na(as.numeric(as.character(filteredMaintenanceEvents$ASYS))),)
nrow(invalidAsysRows)

#Do the conversion of ASYS numbers to actual numbers.  Anything which doesn't convert to a number is an error (should be 127)
filteredMaintenanceEvents <- mutate(filteredMaintenanceEvents, ASYS= as.numeric(as.character(filteredMaintenanceEvents$ASYS)))
nrow(filteredMaintenanceEvents)
```

```{r}
#There are some non-numeric ASYS numbers.  Convert them to numeric and exlcude those that dont parse.
validAsysMaintenanceEvents <- filter(filteredMaintenanceEvents, !is.na(as.numeric(as.character(filteredMaintenanceEvents$ASYS))),)
nrow(validAsysMaintenanceEvents)

# 26 rows with 2017 and non-numeric values in ASYS  (Excel agrees)
# 98 rows with 2017 and blank ASYS  (Excel agrees)

```


```{r}
#There is no property data for January so we'll won't use it
validAsysMaintenanceEventsJan <- validAsysMaintenanceEvents[validAsysMaintenanceEvents$Fault.Identified.Month.Number == 1,]
```

```{r}
validAsysMaintenanceEventsFeb <- validAsysMaintenanceEvents[validAsysMaintenanceEvents$Fault.Identified.Month.Number == 2,]
validAsysMaintenanceEventsMar <- validAsysMaintenanceEvents[validAsysMaintenanceEvents$Fault.Identified.Month.Number == 3,]
validAsysMaintenanceEventsApr <- validAsysMaintenanceEvents[validAsysMaintenanceEvents$Fault.Identified.Month.Number == 4,]
validAsysMaintenanceEventsMay <- validAsysMaintenanceEvents[validAsysMaintenanceEvents$Fault.Identified.Month.Number == 5,]  
validAsysMaintenanceEventsJun <- validAsysMaintenanceEvents[validAsysMaintenanceEvents$Fault.Identified.Month.Number == 6,]  
validAsysMaintenanceEventsJul <- validAsysMaintenanceEvents[validAsysMaintenanceEvents$Fault.Identified.Month.Number == 7,]  
validAsysMaintenanceEventsAug <- validAsysMaintenanceEvents[validAsysMaintenanceEvents$Fault.Identified.Month.Number == 8,]  
validAsysMaintenanceEventsSep <- validAsysMaintenanceEvents[validAsysMaintenanceEvents$Fault.Identified.Month.Number == 9,]  
validAsysMaintenanceEventsOct <- validAsysMaintenanceEvents[validAsysMaintenanceEvents$Fault.Identified.Month.Number == 10,]  
```



```{r}
#FEBRUARY
#load the property data - 2917 rows  (should be 2915)  (the import pulls in two totally blank rows at the end which are filtered out by the ASYS check routine).
rawPropertyDataFeb <- read.csv("csv/Available_Bedrooms_And_Bedspaces_NW_2017-02-01.csv", skip=3, stringsAsFactors = FALSE)

#filter out rows that do not have a valid ASYS value - 5 rows (3 genuine and 2 blanks from import)
validAsysPropertyDataFeb <- filter(rawPropertyDataFeb, !is.na(as.numeric(as.character(rawPropertyDataFeb$ASYS))),)
nrow(validAsysPropertyDataFeb)
#valid row count is correct at 2912 - 5 rows excluded (3 genuine and 2 blanks from import)

#MARCH
#load the property data
rawPropertyDataMar <- read.csv("csv/Available_Bedrooms_And_Bedspaces_NW_2017-03-01.csv", skip=3, stringsAsFactors = FALSE)

#filter out rows that do not have a valid ASYS value
validAsysPropertyDataMar <- filter(rawPropertyDataMar, !is.na(as.numeric(as.character(rawPropertyDataMar$ASYS))),)
nrow(validAsysPropertyDataMar)
#Row count correct at 2931 - 7 blank asys

#APRIL
#load the property data
rawPropertyDataApr <- read.csv("csv/Available_Bedrooms_And_Bedspaces_NW_2017-04-01.csv", skip=3, stringsAsFactors = FALSE)

#filter out rows that do not have a valid ASYS value
validAsysPropertyDataApr <- filter(rawPropertyDataApr, !is.na(as.numeric(as.character(rawPropertyDataApr$ASYS))),)
nrow(validAsysPropertyDataApr)
#Row count correct at 2931 - 3 blank asys


#MAY
#load the property data
rawPropertyDataMay <- read.csv("csv/Available_Bedrooms_And_Bedspaces_NW_2017-05-01.csv", skip=3, stringsAsFactors = FALSE)

#filter out rows that do not have a valid ASYS value
validAsysPropertyDataMay <- filter(rawPropertyDataMay, !is.na(as.numeric(as.character(rawPropertyDataMay$ASYS))),)
nrow(validAsysPropertyDataMay)
#Row count correct at 2933 - 2 blank asys

#JUNE
#load the property data
rawPropertyDataJun <- read.csv("csv/Available_Bedrooms_And_Bedspaces_NW_2017-06-01.csv", skip=3, stringsAsFactors = FALSE)

#filter out rows that do not have a valid ASYS value
validAsysPropertyDataJun <- filter(rawPropertyDataJun, !is.na(as.numeric(as.character(rawPropertyDataJun$ASYS))),)
nrow(validAsysPropertyDataJun)
#Row count correct at 2933 - 9 blank asys

#JUL
#load the property data
rawPropertyDataJul <- read.csv("csv/Available_Bedrooms_And_Bedspaces_NW_2017-07-01.csv", skip=3, stringsAsFactors = FALSE)

#filter out rows that do not have a valid ASYS value
validAsysPropertyDataJul <- filter(rawPropertyDataJul, !is.na(as.numeric(as.character(rawPropertyDataJul$ASYS))),)
nrow(validAsysPropertyDataJul)
#Row count correct at 2934 - 18 blank asys

#AUG
#load the property data
rawPropertyDataAug <- read.csv("csv/Available_Bedrooms_And_Bedspaces_NW_2017-08-01.csv", skip=3, stringsAsFactors = FALSE)

#filter out rows that do not have a valid ASYS value
validAsysPropertyDataAug <- filter(rawPropertyDataAug, !is.na(as.numeric(as.character(rawPropertyDataAug$ASYS))),)
nrow(validAsysPropertyDataAug)
#Row count correct at 2942 - 8 blank asys and 1 marked 'DUPLICATE'

#SEP
#load the property data
rawPropertyDataSep <- read.csv("csv/Available_Bedrooms_And_Bedspaces_NW_2017-09-01.csv", skip=3, stringsAsFactors = FALSE)

#filter out rows that do not have a valid ASYS value
validAsysPropertyDataSep <- filter(rawPropertyDataSep, !is.na(as.numeric(as.character(rawPropertyDataSep$ASYS))),)
nrow(validAsysPropertyDataSep)
#Row count correct at 2935 - 18 blank asys 

#OCT
#load the property data
rawPropertyDataOct <- read.csv("csv/Available_Bedrooms_And_Bedspaces_NW_2017-10-01.csv", skip=3, stringsAsFactors = FALSE)

#filter out rows that do not have a valid ASYS value
validAsysPropertyDataOct <- filter(rawPropertyDataOct, !is.na(as.numeric(as.character(rawPropertyDataOct$ASYS))),)
nrow(validAsysPropertyDataOct)
#Row count correct at 2953 - 5 blank asys 
```


```{r}
#remove negative bedspaces 
validAsysPropertyDataFeb$Negative.Bedspaces <- ifelse(validAsysPropertyDataFeb$Available.Bedspaces < 0, abs(validAsysPropertyDataFeb$Available.Bedspaces), 0)
validAsysPropertyDataFeb$Available.Bedspaces <- ifelse(validAsysPropertyDataFeb$Available.Bedspaces < 0, 0, validAsysPropertyDataFeb$Available.Bedspaces)

#remove negative bedrooms
validAsysPropertyDataFeb$Negative.Bedrooms <- ifelse(validAsysPropertyDataFeb$Available.Bedrooms < 0, abs(validAsysPropertyDataFeb$Available.Bedrooms), 0)
validAsysPropertyDataFeb$Available.Bedrooms <- ifelse(validAsysPropertyDataFeb$Available.Bedrooms < 0, 0, validAsysPropertyDataFeb$Available.Bedrooms)



#remove negative bedspaces 
validAsysPropertyDataMar$Negative.Bedspaces <- ifelse(validAsysPropertyDataMar$Available.Bedspaces < 0, abs(validAsysPropertyDataMar$Available.Bedspaces), 0)
validAsysPropertyDataMar$Available.Bedspaces <- ifelse(validAsysPropertyDataMar$Available.Bedspaces < 0, 0, validAsysPropertyDataMar$Available.Bedspaces)

#remove negative bedrooms
validAsysPropertyDataMar$Negative.Bedrooms <- ifelse(validAsysPropertyDataMar$Available.Bedrooms < 0, abs(validAsysPropertyDataMar$Available.Bedrooms), 0)
validAsysPropertyDataMar$Available.Bedrooms <- ifelse(validAsysPropertyDataMar$Available.Bedrooms < 0, 0, validAsysPropertyDataMar$Available.Bedrooms)


#remove negative bedspaces 
validAsysPropertyDataApr$Negative.Bedspaces <- ifelse(validAsysPropertyDataApr$Available.Bedspaces < 0, abs(validAsysPropertyDataApr$Available.Bedspaces), 0)
validAsysPropertyDataApr$Available.Bedspaces <- ifelse(validAsysPropertyDataApr$Available.Bedspaces < 0, 0, validAsysPropertyDataApr$Available.Bedspaces)

#remove negative bedrooms
validAsysPropertyDataApr$Negative.Bedrooms <- ifelse(validAsysPropertyDataApr$Available.Bedrooms < 0, abs(validAsysPropertyDataApr$Available.Bedrooms), 0)
validAsysPropertyDataApr$Available.Bedrooms <- ifelse(validAsysPropertyDataApr$Available.Bedrooms < 0, 0, validAsysPropertyDataApr$Available.Bedrooms)

#remove negative bedspaces 
validAsysPropertyDataMay$Negative.Bedspaces <- ifelse(validAsysPropertyDataMay$Available.Bedspaces < 0, abs(validAsysPropertyDataMay$Available.Bedspaces), 0)
validAsysPropertyDataMay$Available.Bedspaces <- ifelse(validAsysPropertyDataMay$Available.Bedspaces < 0, 0, validAsysPropertyDataMay$Available.Bedspaces)

#remove negative bedrooms
validAsysPropertyDataMay$Negative.Bedrooms <- ifelse(validAsysPropertyDataMay$Available.Bedrooms < 0, abs(validAsysPropertyDataMay$Available.Bedrooms), 0)
validAsysPropertyDataMay$Available.Bedrooms <- ifelse(validAsysPropertyDataMay$Available.Bedrooms < 0, 0, validAsysPropertyDataMay$Available.Bedrooms)


#remove negative bedspaces 
validAsysPropertyDataJun$Negative.Bedspaces <- ifelse(validAsysPropertyDataJun$Available.Bedspaces < 0, abs(validAsysPropertyDataJun$Available.Bedspaces), 0)
validAsysPropertyDataJun$Available.Bedspaces <- ifelse(validAsysPropertyDataJun$Available.Bedspaces < 0, 0, validAsysPropertyDataJun$Available.Bedspaces)

#remove negative bedrooms
validAsysPropertyDataJun$Negative.Bedrooms <- ifelse(validAsysPropertyDataJun$Available.Bedrooms < 0, abs(validAsysPropertyDataJun$Available.Bedrooms), 0)
validAsysPropertyDataJun$Available.Bedrooms <- ifelse(validAsysPropertyDataJun$Available.Bedrooms < 0, 0, validAsysPropertyDataJun$Available.Bedrooms)


#remove negative bedspaces 
validAsysPropertyDataJul$Negative.Bedspaces <- ifelse(validAsysPropertyDataJul$Available.Bedspaces < 0, abs(validAsysPropertyDataJul$Available.Bedspaces), 0)
validAsysPropertyDataJul$Available.Bedspaces <- ifelse(validAsysPropertyDataJul$Available.Bedspaces < 0, 0, validAsysPropertyDataJul$Available.Bedspaces)

#remove negative bedrooms
validAsysPropertyDataJul$Negative.Bedrooms <- ifelse(validAsysPropertyDataJul$Available.Bedrooms < 0, abs(validAsysPropertyDataJul$Available.Bedrooms), 0)
validAsysPropertyDataJul$Available.Bedrooms <- ifelse(validAsysPropertyDataJul$Available.Bedrooms < 0, 0, validAsysPropertyDataJul$Available.Bedrooms)


#remove negative bedspaces 
validAsysPropertyDataAug$Negative.Bedspaces <- ifelse(validAsysPropertyDataAug$Available.Bedspaces < 0, abs(validAsysPropertyDataAug$Available.Bedspaces), 0)
validAsysPropertyDataAug$Available.Bedspaces <- ifelse(validAsysPropertyDataAug$Available.Bedspaces < 0, 0, validAsysPropertyDataAug$Available.Bedspaces)

#remove negative bedrooms
validAsysPropertyDataAug$Negative.Bedrooms <- ifelse(validAsysPropertyDataAug$Available.Bedrooms < 0, abs(validAsysPropertyDataAug$Available.Bedrooms), 0)
validAsysPropertyDataAug$Available.Bedrooms <- ifelse(validAsysPropertyDataAug$Available.Bedrooms < 0, 0, validAsysPropertyDataAug$Available.Bedrooms)


#remove negative bedspaces 
validAsysPropertyDataSep$Negative.Bedspaces <- ifelse(validAsysPropertyDataSep$Available.Bedspaces < 0, abs(validAsysPropertyDataSep$Available.Bedspaces), 0)
validAsysPropertyDataSep$Available.Bedspaces <- ifelse(validAsysPropertyDataSep$Available.Bedspaces < 0, 0, validAsysPropertyDataSep$Available.Bedspaces)

#remove negative bedrooms
validAsysPropertyDataSep$Negative.Bedrooms <- ifelse(validAsysPropertyDataSep$Available.Bedrooms < 0, abs(validAsysPropertyDataSep$Available.Bedrooms), 0)
validAsysPropertyDataSep$Available.Bedrooms <- ifelse(validAsysPropertyDataSep$Available.Bedrooms < 0, 0, validAsysPropertyDataSep$Available.Bedrooms)


#remove negative bedspaces 
validAsysPropertyDataOct$Negative.Bedspaces <- ifelse(validAsysPropertyDataOct$Available.Bedspaces < 0, abs(validAsysPropertyDataOct$Available.Bedspaces), 0)
validAsysPropertyDataOct$Available.Bedspaces <- ifelse(validAsysPropertyDataOct$Available.Bedspaces < 0, 0, validAsysPropertyDataOct$Available.Bedspaces)

#remove negative bedrooms
validAsysPropertyDataOct$Negative.Bedrooms <- ifelse(validAsysPropertyDataOct$Available.Bedrooms < 0, abs(validAsysPropertyDataOct$Available.Bedrooms), 0)
validAsysPropertyDataOct$Available.Bedrooms <- ifelse(validAsysPropertyDataOct$Available.Bedrooms < 0, 0, validAsysPropertyDataOct$Available.Bedrooms)
```



*Pair faults with property data*
```{r}
#property 2912 rows
#events Feb 11304
propertyEventsFeb <- join(y = validAsysPropertyDataFeb, x = validAsysMaintenanceEventsFeb, by = c("ASYS"), type = "left", match = "all")

#11304 rows in the joined dataset - exactly the number of rows in the events dataset
propertyEventsMar <- join(y = validAsysPropertyDataMar, x = validAsysMaintenanceEventsMar, by = c("ASYS"), type = "left", match = "all")

propertyEventsApr <- join(y = validAsysPropertyDataApr, x = validAsysMaintenanceEventsApr, by = c("ASYS"), type = "left", match = "all")

propertyEventsMay <- join(y = validAsysPropertyDataMay, x = validAsysMaintenanceEventsMay, by = c("ASYS"), type = "left", match = "all")

propertyEventsJun <- join(y = validAsysPropertyDataJun, x = validAsysMaintenanceEventsJun, by = c("ASYS"), type = "left", match = "all")

propertyEventsJul <- join(y = validAsysPropertyDataJul, x = validAsysMaintenanceEventsJul, by = c("ASYS"), type = "left", match = "all")

propertyEventsAug <- join(y = validAsysPropertyDataAug, x = validAsysMaintenanceEventsAug, by = c("ASYS"), type = "left", match = "all")

propertyEventsSep <- join(y = validAsysPropertyDataSep, x = validAsysMaintenanceEventsSep, by = c("ASYS"), type = "left", match = "all")

propertyEventsOct <- join(y = validAsysPropertyDataOct, x = validAsysMaintenanceEventsOct, by = c("ASYS"), type = "left", match = "all")


propertyEvents <- rbind(propertyEventsFeb, propertyEventsMar, propertyEventsApr, propertyEventsMay, propertyEventsJun, propertyEventsJul, propertyEventsAug, propertyEventsSep, propertyEventsOct)


#looks like there are events that dont relate to a property and properties that have had no events (but the later wont be shown in the data set)

#find events with no 'Property.Category' which indicates the property details for the event were not found
eventsWithNoProperty <- filter(propertyEvents, is.na(propertyEvents$Property.Category))

#count number of events by ASYS number  (432 events in total across 25 properties) - we'll exclude them
eventsWithNoPropertyCount <- plyr::count(eventsWithNoProperty, "ASYS")

#exclude merged event row where there are no property details - should be 11304 - 432 = 10872
completeRows <- subset(propertyEvents, !is.na(propertyEvents$Property.Category),)

#There are some blank values in fields that need cleaning up
completeRows$Town[completeRows$Town == ""] <- "Unknown Town"
completeRows$Event.Accommodation.Type[completeRows$Event.Accommodation.Type == ""] <- "Unknown Accommodation Type"
completeRows$Occupancy.Type[completeRows$Occupancy.Type == ""] <- "Unknown Occupancy Type"
```



```{r}
#Need to look at properties MONTHLY - will give us more observations (dont necessarily want to view months tho - we are working with property types, not individual properties).

#CREATE A HISTOGRAM OF NUMBER OF PROPERTIES WITH NUMBER OF FAULTS - MAKE A QUICK SUMMARY BY ASYS
#This will create faults per property per month - loses us some data
propertyEventCount <- plyr::count(completeRows, c("ASYS", "Fault.Identified.Month.Number"))

qplot(propertyEventCount$freq,
      geom="histogram",
      binwidth = 0.5,  
      main = "Histogram for Maintenance Issues", 
      xlab = "Number of Issues",  
      ylab = "Number of Properties",  
      fill=I("blue"), 
      col=I("blue"), 
      alpha=I(.2),
      xlim=c(0,50))

#We have a heavily right skewed distribution so we might need to balance it before we can predict.
#See: https://stats.stackexchange.com/questions/107610/what-is-the-reason-the-log-transformation-is-used-with-right-skewed-distribution
```

```{r}
#Using box plots to explore things that might be related to number of issues,

#We want the number of errors by property type - which is just a row count
#y = count(completeRowsFeb, c('Ward', 'Property.Type'))
#y

y = count(completeRows, c('ASYS', 'Property.Type'))

#Number of errors by property type
propertyTypeBP1 <- ggplot(y, aes(x = Property.Type, y = freq, fill=Property.Type)) +
        scale_x_discrete(name = "Property Type") +
        scale_y_continuous(name = "Issues per Month", breaks = seq(0, 145, 5), limits=c(0, 145)) +
        ggtitle("Boxplot of maintenance events by property type") +
        geom_boxplot()
propertyTypeBP1

```


Looks like there are in general more problems with detached properties.  Flats-Apartments are generally fine but there are a couple of problem properties.  There are a large number of high fault problem properties that are Terraced.




WE'LL PROBABLY NEED TO ADD IN ALL THE PROPERTIES THAT DON'T HAVE AN ERROR OTHERWISE IT WILL ALWAYS SKEW WHEN LEARNING.


```{r}
y = count(completeRows, c('ASYS', 'Event.Accommodation.Type'))

#Number of errors by property type
accomTypeBP1 <- ggplot(y, aes(x = Event.Accommodation.Type, y = freq, fill=Event.Accommodation.Type)) +
        scale_x_discrete(name = "Accommodation Type") +
        scale_y_continuous(name = "Issues per Month", breaks = seq(0, 145, 5), limits=c(0, 145)) +
        ggtitle("Boxplot of maintenance events by accommodation type") +
        geom_boxplot()
accomTypeBP1

```

```{r}
y = count(completeRows, c('ASYS', 'Occupancy.Type'))

#Number of errors by property type
OccupancyTypeBP1 <- ggplot(y, aes(x = Occupancy.Type, y = freq, fill=Occupancy.Type)) +
        scale_x_discrete(name = "Occupancy Type") +
        scale_y_continuous(name = "Issues per Month", breaks = seq(0, 145, 5), limits=c(0, 145)) +
        ggtitle("Boxplot of maintenance events by Occupancy Type") +
        geom_boxplot()
OccupancyTypeBP1

```


```{r}
y = count(completeRows, c('ASYS', 'Town'))

#Number of errors by property type
TownBP1 <- ggplot(y, aes(x = Town, y = freq, fill=Town)) +
        scale_x_discrete(name = "Town") +
        scale_y_continuous(name = "Issues per Month", breaks = seq(0, 145, 5), limits=c(0, 145)) +
        ggtitle("Boxplot of maintenance events by town") +
        geom_boxplot()
TownBP1

```

```{r}
y = count(completeRows, c('ASYS', 'Occupancy'))

#Number of errors by occupancy
OccupancyBP1 <- ggplot(y, aes(x = factor(Occupancy), y = freq, fill=factor(Occupancy))) +
        scale_x_discrete(name = "Occupancy") +
        scale_y_continuous(name = "Issues per Month", breaks = seq(0, 145, 5), limits=c(0, 145)) +
        ggtitle("Boxplot of maintenance events by occupancy") +
        geom_boxplot()
OccupancyBP1


```


*Create ML Data Set - Filter out attributes that wont add anything to our model*
```{r}
#Group by ASYS and month so we have events per property per month.

#should give 19185 rows - but gives 19342 - some property details have changed 'in month'.
#I think these are still valid observations that should be kept.

mlSet = count(completeRows, c(
'ASYS',
'Property.Status.at.Capture',
'No.of.Occupants',
'Event.Accommodation.Type',
'Property.Category',
'Town',
'Property.Type',
'Accommodation.Type',
'Occupancy.Type',
'Property.Status',
'Bed.rooms',
'Bedspaces',
'Active.Service.Users',
'Active.Service.Users.Plus',
'Available.Bedrooms',
'Available.Bedspaces',
'Occupancy',
'Rent',
'Lease.Type',
'No.Area.Bedrooms',
'Total.Calculated.Bedspaces',
'No.Area.Lounges',
'No.Area.Dining.Rooms',
'No.Area.Kitchens',
'No.Area.Kitchen.Diners',
'No.Area.Utilities',
'No.Area.W.C.s',
'No.Area.Bathrooms',
'No.Area.Ensuites',
'No.Floors',
'Negative.Bedspaces',
'Negative.Bedrooms',
'Fault.Identified.Month.Number'
))

#remove the property identifier and the month - we dont need them and they may influence learning
mlSet <- mlSet[ , names(mlSet) != "ASYS"]
mlSet <- mlSet[ , names(mlSet) != "Fault.Identified.Month.Number"]

#Removed 'Landlord.Company.Name' from the dataset because it generates lots of columns and doesn't seem to be very important for predicting faults.
#!Removed Ward - because its troublesome - might bring it back in later

#mlSet
ggplot(mlSet, aes(x=No.of.Occupants, y=freq)) + geom_point()
```


Starting Machine Learning
-------------------------
We want to use linear regression and predict the number of issues based on location, occupancy, occupant type and property type with 85% accuracy.

```{r}
#basic stats
summary(mlSet)

#complete roles - no output here means all the rows have values in every column
mlSet <- mlSet[complete.cases(mlSet),]
mlSet[!complete.cases(mlSet),]
```

The variable 'mlSet' not contains all the data you need to start buidling models.

